Hydras \& Co.

### 2022-07-28 doc/chapter-primrec.tex
small changes
JFLA Slides (draft)
revision book (-> p. 28)
work on Ackermann (proof scripts + book)

  Getting rid of the term \texttt{x-x}, we generate two easy-to-solve sub-goals.

@@

\index{primrec}{Predicates!isPR}
\index{coq}{Extensionally equal functions}

@@

\begin{remark}
In the library \texttt{primRec}, all these lemmas are opaque (registered with \texttt{Qed}. Thus they do not allow the user to look at the witness of a proof of a \texttt{isPR} statement. Our example of page~\pageref{sect:bigfac} was built using a  copy of \texttt{primRec.v} where many \texttt{Qed}s have been replaced with
\texttt{Defined}s.

@@

The constructors \texttt{zeroFunc}, \texttt{succFunc},  and \texttt{projFunc} of type
\texttt{PrimRec} allows us to write trivial proofs of primitive recursivity. 
Although  the following lemmas are already proven in 
\href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec},
we wrote alternate proofs in 
\href{../theories/html/hydras.MoreAck.PrimRecExamples.html}%
{Ackermann.MoreAck.PrimRecExamples.v}, in order to illustrate the main proof patterns.

@@

\input{movies/snippets/PrimRecExamples/SuccIsPR}

@@

\input{movies/snippets/primRec/SchemePrimRecInd}

>>>>

  Getting rid of the term \texttt{x-x}, we generate two easy-to-solve subgoals.

@@

\index{primrec}{Predicates!isPR}
%\index{coq}{Extensionally equal functions}

@@

\begin{remark}
In the library \texttt{primRec}, all these lemmas are opaque (registered with \texttt{Qed}). Thus they do not allow the user to look at the witness of a proof of a \texttt{isPR} statement. Our example of page~\pageref{sect:bigfac} was built using a  copy of \texttt{primRec.v} where many \texttt{Qed}s have been replaced with
\texttt{Defined}s.

@@

The constructors \texttt{zeroFunc}, \texttt{succFunc},  and \texttt{projFunc} of type
\texttt{PrimRec} allows us to write trivial proofs of primitive recursivity. 
Some of   the following lemmas are already proven in 
\href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}. More examples are given in 
\href{../theories/html/hydras.MoreAck.PrimRecExamples.html}%
{Ackermann.MoreAck.PrimRecExamples.v}, in order to illustrate the main proof patterns.

@@

\input{movies/snippets/primRec/SuccIsPR}

@@

\inputsnippets{primRec/SchemePrimRecInd,
primRec/SchemePrimRecInda}
